Is it Better to be a Moose or a Black Bear?

### 2024-04-22 paper/paper.qmd
Finished simulation and data testing scripts as well as running Lintr on all scripts

The original data set for moose hunting and harvests obtained from the Ontario Data Catalogue contained seven variables. The first variable,*WMU*, is the Wildlife Management Unit which indicates the specific region in Ontario. There are a total of 95 different WMUs which are grouped into three larger regions, northern, southeastern, and southwestern Ontario. The second variable, *Year*, indicates the harvest year. *Active Hunter* (see @fig-huntersmoose) indicates how many hunters were active in that specific WMU and year. *Bull Harvest*, *Cow Harvest*, and *Calf Harvest* (see @fig-harvestmoosetypes) indicate the respective number of harvests for each type of moose for that specific WMU and year. *Total Harvest* (see @fig-harvestmoose) is the sum of all bull, cow, and calf harvests for that specific WMU and year. The original data set for black bear hunting and harvests contains the same variables of WMU, year, and active hunters (see @fig-huntersbear). However, instead of bull, cow, calf, and total harvest there is only one harvest variable called *Harvest* (see @fig-harvestbear) as all black bears are grouped as one.

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_moose, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_moose, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_moose, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot()+
  geom_line(data = types_moose, aes(x = Year, y = `Cow Harvest`), color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = types_moose, aes(x = Year, y = `Calf Harvest`), color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = types_moose, aes(x = Year, y = `Bull Harvest`), color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`), color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`), color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`), color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_bear, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_bear, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_bear, aes(x = Year, y = `Active Hunters`), color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_bear, aes(x = Year, y = Harvest), color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_bear, aes(x = Year, y = Harvest), color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_bear, aes(x = Year, y = Harvest), color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

#create line graph 
ggplot()+
  geom_line(data = north_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`), color = "red")+
  theme_minimal()

@@

#create line graph 
ggplot()+
  geom_line(data = se_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`), color = "red")+
  theme_minimal()

@@

#create line graph 
ggplot()+
  geom_line(data = sw_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`), color = "red")+
  theme_minimal()

@@

#create line graph 
ggplot()+
  geom_line(data = sw_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = se_bear, aes(x = Year, y = Harvest), color = "red")+
  geom_line(data = north_bear, aes(x = Year, y = Harvest), color = "green")+
  theme_minimal()
```

@@

#create line graph 
ggplot()+
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`), color = "blue") + 
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`), color = "red")+
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`), color = "green")+
  theme_minimal()
```

@@

#create line graph 
ggplot()+
  geom_line(data = sw_bear, aes(x = Year, y = `Active Hunters`), color = "blue") +
  geom_line(data = sw_moose, aes(x = Year, y = `Active Hunters`), color = "red")+
  theme_minimal()

@@

#create line graph 
ggplot()+
  geom_line(data = se_bear, aes(x = Year, y = `Active Hunters`), color = "blue") +
  geom_line(data = se_moose, aes(x = Year, y = `Active Hunters`), color = "red")+
  theme_minimal()

@@

#create line graph 
ggplot()+
  geom_line(data = north_bear, aes(x = Year, y = `Active Hunters`), color = "blue") +
  geom_line(data = north_moose, aes(x = Year, y = `Active Hunters`), color = "red")+
  theme_minimal()

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_moose, aes(x = `Active Hunters`, y = `Total Harvest`), color = "red") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_moose, aes(x = `Active Hunters`, y = `Total Harvest`), color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_moose, aes(x = `Active Hunters`, y = `Total Harvest`), color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "C")

@@

plot1 <- 
  ggplot()+
  geom_line(data = north_bear, aes(x = `Active Hunters`, y = Harvest), color = "blue") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "A")

plot2 <-
  ggplot()+
  geom_line(data = se_bear, aes(x = `Active Hunters`, y = Harvest), color = "blue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "B")

plot3 <-
  ggplot()+
  geom_line(data = sw_bear, aes(x = `Active Hunters`, y = Harvest), color = "blue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70))+
  labs(tag = "C")

@@

#create line graph 
ggplot(all_moose, aes(x = `Active Hunters`, y = `Total Harvest`, color = WMU))+
scale_color_distiller(palette = "RdPu")+
geom_point(show.legend = TRUE)+
theme_minimal()
```

@@

#create line graph 
ggplot(all_bear, aes(x = `Active Hunters`, y = Harvest, color = WMU))+
geom_point(show.legend = TRUE)+
scale_color_distiller(palette = "YlGnBu")+
theme_minimal()
```

>>>>

The original data set for moose hunting and harvests obtained from the Ontario Data Catalogue contained seven variables. The first variable,*WMU*, is the Wildlife Management Unit which indicates the specific region in Ontario. There are a total of 95 different WMUs which are grouped into three larger regions, northern, southeastern, and southwestern Ontario. However, the black bear data set only has data from WMUs 1 through 82 and the moose data set has data from WMUs 1-65. The second variable, *Year*, indicates the harvest year. *Active Hunter* (see @fig-huntersmoose) indicates how many hunters were active in that specific WMU and year. *Bull Harvest*, *Cow Harvest*, and *Calf Harvest* (see @fig-harvestmoosetypes) indicate the respective number of harvests for each type of moose for that specific WMU and year. *Total Harvest* (see @fig-harvestmoose) is the sum of all bull, cow, and calf harvests for that specific WMU and year. The original data set for black bear hunting and harvests contains the same variables of WMU, year, and active hunters (see @fig-huntersbear). However, instead of bull, cow, calf, and total harvest there is only one harvest variable called *Harvest* (see @fig-harvestbear) as all black bears are grouped as one.

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_moose, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_moose, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_moose, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot() +
  geom_line(data = types_moose, aes(x = Year, y = `Cow Harvest`),
            color = "black") +
  theme_minimal()+
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = types_moose, aes(x = Year, y = `Calf Harvest`),
            color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = types_moose, aes(x = Year, y = `Bull Harvest`),
            color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`),
            color = "black") +
  theme_minimal() +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`),
            color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`),
            color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_bear, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_bear, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_bear, aes(x = Year, y = `Active Hunters`),
            color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_bear, aes(x = Year, y = Harvest),
            color = "black") +
  theme_minimal() +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_bear, aes(x = Year, y = Harvest),
            color = "black") +
  theme_minimal() +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_bear, aes(x = Year, y = Harvest),
            color = "black") +
  theme_minimal() +
  labs(tag = "C")

@@

#create line graph 
ggplot() +
  geom_line(data = north_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`),
            color = "red") +
  theme_minimal()

@@

#create line graph 
ggplot() +
  geom_line(data = se_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`),
            color = "red") +
  theme_minimal()

@@

#create line graph 
ggplot() +
  geom_line(data = sw_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`),
            color = "red") +
  theme_minimal()

@@

#create line graph 
ggplot() +
  geom_line(data = sw_bear, aes(x = Year, y = Harvest), color = "blue") + 
  geom_line(data = se_bear, aes(x = Year, y = Harvest), color = "red") +
  geom_line(data = north_bear, aes(x = Year, y = Harvest), color = "green") +
  theme_minimal()
```

@@

#create line graph 
ggplot() +
  geom_line(data = sw_moose, aes(x = Year, y = `Total Harvest`),
            color = "blue") + 
  geom_line(data = se_moose, aes(x = Year, y = `Total Harvest`),
            color = "red") +
  geom_line(data = north_moose, aes(x = Year, y = `Total Harvest`),
            color = "green") +
  theme_minimal()
```

@@

#create line graph 
ggplot() +
  geom_line(data = sw_bear, aes(x = Year, y = `Active Hunters`),
            color = "blue") +
  geom_line(data = sw_moose, aes(x = Year, y = `Active Hunters`),
            color = "red") +
  theme_minimal()

@@

#create line graph 
ggplot() +
  geom_line(data = se_bear, aes(x = Year, y = `Active Hunters`),
            color = "blue") +
  geom_line(data = se_moose, aes(x = Year, y = `Active Hunters`),
            color = "red") +
  theme_minimal()

@@

#create line graph 
ggplot() +
  geom_line(data = north_bear, aes(x = Year, y = `Active Hunters`),
            color = "blue") +
  geom_line(data = north_moose, aes(x = Year, y = `Active Hunters`),
            color = "red") +
  theme_minimal()

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_moose, aes(x = `Active Hunters`, y = `Total Harvest`),
            color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_moose, aes(x = `Active Hunters`, y = `Total Harvest`),
            color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_moose, aes(x = `Active Hunters`, y = `Total Harvest`),
            color = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "C")

@@

plot1 <- 
  ggplot() +
  geom_line(data = north_bear, aes(x = `Active Hunters`, y = Harvest),
            color = "blue") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "A")

plot2 <-
  ggplot() +
  geom_line(data = se_bear, aes(x = `Active Hunters`, y = Harvest),
            color = "blue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "B")

plot3 <-
  ggplot() +
  geom_line(data = sw_bear, aes(x = `Active Hunters`, y = Harvest),
            color = "blue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 70)) +
  labs(tag = "C")

@@

#create line graph 
ggplot(all_moose, aes(x = `Active Hunters`, y = `Total Harvest`, color = WMU)) +
scale_color_distiller(palette = "RdPu") +
geom_point(show.legend = TRUE) +
theme_minimal()
```

@@

#create line graph 
ggplot(all_bear, aes(x = `Active Hunters`, y = Harvest, color = WMU)) +
geom_point(show.legend = TRUE) +
scale_color_distiller(palette = "YlGnBu") +
theme_minimal()
```
